
\documentclass[12pt]{article}
\title{The Dhammapada: A Collection of Verses: Being One of the Canonical Books of the Buddhists}
\usepackage[bmargin=.25in, lmargin=.25in, rmargin=.25in, tmargin=.25in, paperwidth=4.25in, paperheight=5.5in]{geometry}
\usepackage{graphicx}
\begin{document}
\thispagestyle{empty}
\begin{center}
\textbf{\Large The Dhammapada: A Collection of Verses: Being One of the Canonical Books of the Buddhists}\\
\textbf{Friedrich Max M\"{u}ller}\\

\end{center}

 All that we are is the result of what we have thought: it is 
founded on our thoughts, it is made up of our thoughts.  If a man
speaks or acts with an evil thought, pain follows him, as the wheel
follows the foot of the ox that draws the carriage.


 All that we are is the result of what we have thought: it is
founded on our thoughts, it is made up of our thoughts.  If a man
speaks or acts with a pure thought, happiness follows him, like a
shadow that never leaves him.


 ``He abused me, he beat me, he defeated me, he robbed me,"--in those
who harbour such thoughts hatred will never cease.


 ``He abused me, he beat me, he defeated me, he robbed me,"--in those
who do not harbour such thoughts hatred will cease.


 For hatred does not cease by hatred at any time: hatred ceases by
love, this is an old rule.


 The world does not know that we must all come to an end here;--but
those who know it, their quarrels cease at once.


 He who lives looking for pleasures only, his senses uncontrolled,
immoderate in his food, idle, and weak, Mara (the tempter) will
certainly overthrow him, as the wind throws down a weak tree.


 He who lives without looking for pleasures, his senses well
controlled, moderate in his food, faithful and strong, him Mara will
certainly not overthrow, any more than the wind throws down a rocky
mountain.


 He who wishes to put on the yellow dress without having cleansed
himself from sin, who disregards temperance and truth, is unworthy of
the yellow dress.


 But he who has cleansed himself from sin, is well grounded in all
virtues, and regards also temperance and truth, he is indeed worthy of
the yellow dress.


 They who imagine truth in untruth, and see untruth in truth, never
arrive at truth, but follow vain desires.


 They who know truth in truth, and untruth in untruth, arrive at
truth, and follow true desires.


 As rain breaks through an ill-thatched house, passion will break
through an unreflecting mind.


 As rain does not break through a well-thatched house, passion will
not break through a well-reflecting mind.


 The evil-doer mourns in this world, and he mourns in the next; he
mourns in both.  He mourns and suffers when he sees the evil of his
own work.


 The virtuous man delights in this world, and he delights in the
next; he delights in both.  He delights and rejoices, when he sees the
purity of his own work.


 The evil-doer suffers in this world, and he suffers in the next;
he suffers in both.  He suffers when he thinks of the evil he has
done; he suffers more when going on the evil path.


 The virtuous man is happy in this world, and he is happy in the
next; he is happy in both.  He is happy when he thinks of the good he
has done; he is still more happy when going on the good path.


 The thoughtless man, even if he can recite a large portion (of the
law), but is not a doer of it, has no share in the priesthood, but is
like a cowherd counting the cows of others.


 The follower of the law, even if he can recite only a small
portion (of the law), but, having forsaken passion and hatred and
foolishness, possesses true knowledge and serenity of mind, he, caring
for nothing in this world or that to come, has indeed a share in the
priesthood.




\vfill
\begin{center}
{\fontfamily{phv}\selectfont 
Modern Hacker Library\\books.modernhacker.com}
\end{center}
\end{document}
